Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-04 longSC.tex
vn in appendix

\begin{figure*}
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels. The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels. The systematic uncertainties of SC(3,2) and SC(4,2) are not shown for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

>>>>

\begin{figure*}
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/fig4_QConly_ptdep_All.eps}}
        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown on the left panels. The normalized SC(3,2) and SC(4,2) ((b) and (d)) are shown on the right panels. Systematic uncertainties are represented with boxes. The systematic uncertainties of SC(3,2) and SC(4,2) are not shown for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

\newpage

\appendix
\section{Model comparison of the Individual $v_n$}

While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do a quantitative comparison of individual flow harmonics $v_n$ to the various models.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}
